%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Rajnish}{Singh}{ \urlstyle{same} +91 8808100876 | 
\href{rajnish42413@gmail.com}{rajnish42413@gmail.com} |
\href{github.com/rajnish42413}{Github://rajnish42413}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{KIET GROUP OF INSTITUTIONS}
\descript{Bachelor of Information Technology}
\location{2015-2019 | Ghaziabad,UttarPradesh}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/rajnish42413}{\bf rajnish42413} \\
StackOverflow:// \href{https://stackoverflow.com/story/rajnish42413}{\bf rajnish42413} \\
LinkedIn://  \href{https://www.linkedin.com/in/rajnish42413}{\bf rajnish42413} \\
Twitter://  \href{https://twitter.com/rajnish42413}{\bf @rajnish42413} \\
Expo://  \href{https://expo.io/@rajnish42413}{\bf @rajnish42413} \\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Front-End Web Development with React | May 2020 | Coursera
React Native: Advanced Concepts | March 2020 | Udemy
AWS Fundamentals: Going Cloud-Native | August 2019 | Coursera
Linux Level Up | June 2019 | Udemy
HTML, CSS, and Javascript for Web Developers | Jan 2017 | Coursera
\sectionsep

\subsection{Graduation}
Algorithms and Data Structure \\
Operating Systems \\
Artificial Intelligence \\
Hadoop and Big Data \\
Functional Programming \\
Multimedia \\
Database Management \\
Web Technologies
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\textbullet{} Javascript \\
\textbullet{} Python \\
\textbullet{} C/C++ \\
\textbullet{} PHP \\
\textbullet{} CSS \\
\textbullet{} HTML \\
\sectionsep
\subsection{Familiar}
 \textbullet{} Reactjs \\
 \textbullet{} Nodejs \\
 \textbullet{} Redux \\
 \textbullet{} Angularjs | Angular 2+ \\
 \textbullet{} Laravel and Codeigniter \\
 \textbullet{} MySQL and MongoDB \\
 \textbullet{} ReactNative and Ionic \\
 \textbullet{} AWS \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{BigRadar}
\descript{| Software Engineer }
\location{Jun 2019 - Present | Connaught Place, New Delhi}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Working on flexiSpaces,coworly website and mobile applications. 
\item Responsible for creating rest API to interact with a mobile app.
\item Creating IOS and Andriod app on react-native from scratch, and publish to store.
\item Technologies used - Rest API, Reactjs,Nodejs, React Native ,TypeScript and Redux.
\end{tightemize}
\sectionsep

\runsubsection{Genz360}
\descript{| Software Engineer , Part-time }
\location{Mar 2019 - Mar 2020 | Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Responsible for creating rest API to interact with a mobile app.
\item Creating react-native applications for influencers and brands from scratch, and publish to store.
\item Technologies used - Reactjs,Nodejs, React Native ,TypeScript ,Laravel and AntDesign RN.
\end{tightemize}
\sectionsep

\runsubsection{Upstur India}
\descript{| Software Engineering Intern }
\location{Feb 2019 – June 2019 | New Delhi}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Full-stack developer - Wrote and reviewed code of upstur website.
\item Implemented new design from given PSD design.
\end{tightemize}
\sectionsep

\runsubsection{STUDENTING ERA}
\descript{| Web Development Intern }
\location{Sep 2017 – Feb 2018 | Okhla, New Delhi}
\begin{tightemize}
\item I created and Designed the "Certify in India Wesbite" and more in PHP ,HTML ,CSS and more.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{COVID19 AWARENESS AND LIVE STATICS}
\descript{| Self-Made Project}
\location{May 2020 | New Delhi}
A react native application that tracks and visualizes the spread of the covid-19 virus over time in the world and India.  \\
And also get NEWS related to the coronavirus from all over the globe\\
Source Code - https://github.com/rajnish42413/covid-19-live-status
\sectionsep

\runsubsection{Pizza Maker - customize Your Pizza}
\descript{| Self-Made Project}
\location{Sep 2019 | New Delhi}
A Reactjs and Nextjs applicaton for customize your top 10 pizza from list . \\ 
Source Code - https://github.com/rajnish42413/pizza-front
\sectionsep

\runsubsection{E-learning and 2016-2017 KIET Website}
\descript{| College Project}
\location{Mar 2012 – May 2013 | Ithaca, NY}
E-Learning - A platform for teachers to learn and share their great heap of knowledgeA platform for student to learn everything on a single portal. \\
Me and \textbf{\href{https://www.linkedin.com/in/shivam-gupta-js-developer/}{Shivam Gupta}} created e-laerning portal for kiet students and teachers and KIET 2016-17 Website. 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2017	     & top 1st/500+  & KIET Innotech'16 -17| Web Design \\
2018	     & top 1st/500+  & KIET Innotech'17 -18| Web Design \\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
